Live Functional Programming with Typed Holes

### 2018-03-07 calculus.tex
"Substitution Typing"

%% \begin{figure}[!ht]
  \begin{definition}
    $\hasType{\Delta}{\hGamma}{\sigma}{\hGamma'}$ iff $\domof{\sigma} = \domof{\Gamma'}$ and for each $\dexp/x \in \sigma$, we have $x : \htau \in \hGamma'$ and $\hasType{\Delta}{\hGamma}{\dexp}{\htau}$.
  \end{definition}
%%   \caption{substitution type assignment}
%% \end{figure}

@@

\subsection{Metatheory: Correctness of Edit-and-Resume}

>>>>

%% \begin{figure}[!ht]
  \begin{definition}[Substitution Typing]
    $\hasType{\Delta}{\hGamma}{\sigma}{\hGamma'}$ iff $\domof{\sigma} = \domof{\Gamma'}$ and for each $\dexp/x \in \sigma$, we have $x : \htau \in \hGamma'$ and $\hasType{\Delta}{\hGamma}{\dexp}{\htau}$.
  \end{definition}
%%   \caption{substitution type assignment}
%% \end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Metatheory: Correctness of Edit-and-Resume}
\label{sec:resumption}
